---
title: "Brynn"
output:
  word_document: default
  html_document: default
---
##A. CoInvasion

#1.Data Manipulation
```{r}
InVitro <- read.csv("RatioStudy.csv")
names(InVitro)[1] <- "Ratio"
library(multcomp)
library(lsmeans)

```
```{r}
## Summarizes data.
## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
    library(plyr)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}

```

#1. Graphs
##Death Plot
```{r}
library(survival)
InVitro$SurvObj <- with(InVitro, Surv(DeathDay, Survived == 0))

#png("InVitroSurvival.png", width=6, height=6, units="in", res=400)
Survival <- survfit(SurvObj ~ Ratio, data = InVitro)
plot(Survival, col=c("#66CCEE", "#EE6677", "#4477AA"), lty=1, lwd = 3,ylim=c(0.6,1), xlim=c(-1.5,10), xlab="Time (days)", ylab="Proportion Survived")
legend("bottomleft", c("One to One", "One to Two", "One to Four"), col=c("#66CCEE", "#EE6677", "#4477AA"), lty=1, lwd = 3, title="Ratio")
#dev.off()

```
##Reproduction Plot 
```{r}
Invitro1 <- subset(InVitro, Reproduced > -1)
Invitro2 <- subset(Invitro1, Survived == 1)
SummaryRep <- summarySE(Invitro1, measurevar="Reproduced", groupvars="Ratio")
SummarySurv <- summarySE(InVitro, measurevar="Survived", groupvars="Ratio")

plot(1:3, SummaryRep[,3], xaxt="n", ylim=c(0,1), xlim=c(.8,3.2), type="b", pch=16, col="blue", xlab="Treatment", ylab="Proportion Reproduced", cex=1.5, lty=0, cex.lab=1.5, lwd=2)
axis(1, 1:3, labels=c("1:1", "2:1", "4:1"))
arrows(1:3, SummaryRep[,3]-SummaryRep[,"se"], 1:3, SummaryRep[,3]+SummaryRep[, "se"], code=3, angle=90, length=0.05, lwd=2, col="blue")
```

#2.Significance
##Survival
```{r}
model<-glm(Survived~Ratio,family=binomial(link='logit'),data=InVitro)
anova(model, test="Chisq")
summary(model)



library(survival)

#This is the code for survival analysis, it will not run when all of the ones on the final day survived, so Kaylin's suggestion will work
#survdiff(Surv(DeathDay, Survived) ~ Ratio, InVitro)

#This is the analysis for death day if all survived from the final day.
model<-glm(DeathDay~Ratio,family=poisson(link='log'),data=Invitro2)
anova(model, test="Chisq")
summary(model)

```

##Reproduction
```{r}
Rmodel<-glm(Reproduced~Ratio,family=binomial(link='logit'),data=InVitro)
anova(Rmodel, test="Chisq")
summary(Rmodel)

lsm<-lsmeans(Rmodel, list( ~ Ratio))
cld(lsm)
```


##B. Larvae Stage
#1.Data Manipulation
```{r}
Larvae<- read.csv("LarvaeStage.csv")
names(Larvae)[1] <- "Stage"


```

#1. Graphs
##Death Plot
```{r}
library(survival)
Larvae$SurvObj <- with(Larvae, Surv(DeathDay, Survived == 0))

#png("InVitroSurvival.png", width=6, height=6, units="in", res=400)
Survival <- survfit(SurvObj ~ Stage, data = Larvae)
plot(Survival, col=c("#66CCEE", "#EE6677", "#4477AA"), lty=1, lwd = 3,ylim=c(0.6,1), xlim=c(-1.5,10), xlab="Time (days)", ylab="Proportion Survived")
legend("bottomleft", c("Capped", "Uncapped"), col=c("#66CCEE", "#EE6677"), lty=1, lwd = 3, title="Stage")
#dev.off()

```
##Reproduction Plot 
```{r}
SummaryRep1 <- summarySE(Larvae, measurevar="Reproduced", groupvars="Stage")

Larvae1 <- subset(Larvae, Reproduced > -1)
Larvae2 <- subset(Larvae1, Survived == 1)
SummaryRep <- summarySE(Larvae1, measurevar="Reproduced", groupvars="Stage")
SummarySurv <- summarySE(Larvae, measurevar="Survived", groupvars="Stage")

plot(1:2, SummaryRep1[,3], xaxt="n", ylim=c(0,.7), xlim=c(.8,2.2), type="b", pch=16, col="blue", xlab="Treatment", ylab="Proportion Reproduced", cex=1.5, lty=0, cex.lab=1.5, lwd=2)
axis(1, 1:2, labels=c("Capped", "Uncapped"))
arrows(1:2, SummaryRep1[,3]-SummaryRep1[,"se"], 1:2, SummaryRep1[,3]+SummaryRep1[, "se"], code=3, angle=90, length=0.05, lwd=2, col="blue")
```
#2.Significance
##Survival
```{r}
model<-glm(Survived~Stage,family=binomial(link='logit'),data=Larvae)
anova(model, test="Chisq")
summary(model)



library(survival)

#This is the code for survival analysis, it will not run when all of the ones on the final day survived, so Kaylin's suggestion will work
#survdiff(Surv(DeathDay, Survived) ~ Ratio, InVitro)

#This is the analysis for death day if all survived from the final day.
model<-glm(DeathDay~Stage,family=poisson(link='log'),data=Larvae1)
anova(model, test="Chisq")
summary(model)

```
```{r}
Rmodel<-glm(Reproduced~Stage,family=binomial(link='logit'),data=Larvae2)
anova(Rmodel, test="Chisq")
summary(Rmodel)

lsm<-lsmeans(Rmodel, list( ~ Stage))
cld(lsm)
```

##B. Larvae Source
#1.Data Manipulation
```{r}
Larva<- read.csv("LarvaeSource.csv")
names(Larva)[1] <- "Source"


```

#1. Graphs
##Death Plot
```{r}
library(survival)
Larva$SurvObj <- with(Larva, Surv(DeathDay, Survived == 0))

#png("InVitroSurvival.png", width=6, height=6, units="in", res=400)
Survival <- survfit(SurvObj ~ Source, data = Larva)
plot(Survival, col=c("#66CCEE", "#EE6677",  "green", "orange", "purple"), lty=1, lwd = 3,ylim=c(0.6,1), xlim=c(-1.5,10), xlab="Time (days)", ylab="Proportion Survived")
legend("bottomleft", c("One", "Two", "Three", "Four", "Five"), col=c("#66CCEE", "#EE6677", "green","orange", "purple"), lty=1, lwd = 3, title="Source")
#dev.off()

```
##Reproduction Plot 
```{r}
SummaryRep1 <- summarySE(Larva, measurevar="Reproduced", groupvars="Source")

Larva1 <- subset(Larva, Reproduced > -1)
Larva2 <- subset(Larva1, Survived == 1)
SummaryRep <- summarySE(Larva1, measurevar="Reproduced", groupvars="Source")
SummarySurv <- summarySE(Larva, measurevar="Survived", groupvars="Source")

plot(1:5, SummaryRep1[,3], xaxt="n", ylim=c(0,.5), xlim=c(.8,5), type="b", pch=16, col="blue", xlab="Treatment", ylab="Proportion Reproduced", cex=1.5, lty=0, cex.lab=1.5, lwd=2)
axis(1, 1:5, labels=c("One", "Two", "Three","Four","Five"))
arrows(1:5, SummaryRep1[,3]-SummaryRep1[,"se"], 1:5, SummaryRep1[,3]+SummaryRep1[, "se"], code=3, angle=90, length=0.05, lwd=2, col="blue")
```
#2.Significance
##Survival
```{r}
model<-glm(Survived~Source,family=binomial(link='logit'),data=Larva)
anova(model, test="Chisq")
summary(model)

lsm<-lsmeans(model, list( ~ Source))
cld(lsm)

library(survival)

#This is the code for survival analysis, it will not run when all of the ones on the final day survived, so Kaylin's suggestion will work
#survdiff(Surv(DeathDay, Survived) ~ Ratio, InVitro)

#This is the analysis for death day if all survived from the final day.
model<-glm(DeathDay~Source,family=poisson(link='log'),data=Larva2)
anova(model, test="Chisq")
summary(model)

```
```{r}
Rmodel<-glm(Reproduced~Source,family=binomial(link='logit'),data=Larva2)
anova(Rmodel, test="Chisq")
summary(Rmodel)

lsm<-lsmeans(Rmodel, list( ~ Source))
cld(lsm)
```

##B. Mite Stage
#1.Data Manipulation
```{r}
Mite<- read.csv("MStage.csv")
names(Mite)[1] <- "Stage2"

unique(Mite$Stage2)

```

#1. Graphs
##Death Plot
```{r}
library(survival)
Mite$SurvObj <- with(Mite, Surv(DeathDay, Survived == 0))

#png("InVitroSurvival.png", width=6, height=6, units="in", res=400)
Survival <- survfit(SurvObj ~ Stage2, data = Mite)
plot(Survival, col=c("#66CCEE", "#EE6677",  "green", "orange"), lty=1, lwd = 3,ylim=c(0.6,1), xlim=c(-1.5,10), xlab="Time (days)", ylab="Proportion Survived")
legend("bottomleft", c("AAC", "LAC", "AC", "LC"), col=c("#66CCEE", "#EE6677", "green","orange"), lty=1, lwd = 3, title="Stage2")
#dev.off()

```
##Reproduction Plot 
```{r}
SummaryRep1 <- summarySE(Mite, measurevar="Reproduced", groupvars="Stage2")

Mite1 <- subset(Mite, Reproduced > -1)
Mite2 <- subset(Mite1, Survived==1)
SummaryRep <- summarySE(Mite1, measurevar="Reproduced", groupvars="Stage2")
SummarySurv <- summarySE(Mite, measurevar="Survived", groupvars="Stage2")

plot(1:4, SummaryRep1[,3], xaxt="n", ylim=c(0,.5), xlim=c(.8,5), type="b", pch=16, col="blue", xlab="Treatment", ylab="Proportion Reproduced", cex=1.4, lty=0, cex.lab=1.5, lwd=2)
axis(1, 1:4, labels=c("AAC", "LAC", "AC","LC"))
arrows(1:4, SummaryRep1[,3]-SummaryRep1[,"se"], 1:4, SummaryRep1[,3]+SummaryRep1[, "se"], code=3, angle=90, length=0.05, lwd=2, col="blue")
```
#2.Significance
##Survival
```{r}
model<-glm(Survived~Stage2,family=binomial(link='logit'),data=Mite)
anova(model, test="Chisq")
summary(model)

lsm<-lsmeans(model, list( ~ Stage2))
cld(lsm)

library(survival)

#This is the code for survival analysis, it will not run when all of the ones on the final day survived, so Kaylin's suggestion will work
#survdiff(Surv(DeathDay, Survived) ~ Ratio, InVitro)

#This is the analysis for death day if all survived from the final day.
model<-glm(DeathDay~Stage2,family=poisson(link='log'),data=Mite2)
anova(model, test="Chisq")
summary(model)

```
```{r}
Rmodel<-glm(Reproduced~Stage2,family=binomial(link='logit'),data=Mite2)
anova(Rmodel, test="Chisq")
summary(Rmodel)

lsm<-lsmeans(Rmodel, list( ~ Stage2))
cld(lsm)
```

##B. Temperature
#1.Data Manipulation
```{r}
Temp<- read.csv("Temperature.csv")
names(Temp)[1] <- "Stage3"

unique(Temp$Stage3)

```

#1. Graphs
##Death Plot
```{r}
library(survival)
Temp$SurvObj <- with(Temp, Surv(DeathDay, Survived == 0))

#png("InVitroSurvival.png", width=6, height=6, units="in", res=400)
Survival <- survfit(SurvObj ~ Stage3, data = Temp)
plot(Survival, col=c("#66CCEE", "#EE6677",  "green", "orange"), lty=1, lwd = 3,ylim=c(0.6,1), xlim=c(-1.5,10), xlab="Time (days)", ylab="Proportion Survived")
legend("bottomleft", c("30.5", "32.5", "34.5", "36.5"), col=c("#66CCEE", "#EE6677", "green","orange"), lty=1, lwd = 3, title="Temperatures")
#dev.off()

```
##Reproduction Plot 
```{r}
SummaryRep1 <- summarySE(Temp, measurevar="Reproduced", groupvars="Stage3")

Temp1 <- subset(Temp, Reproduced > -1)
SummaryRep <- summarySE(Temp1, measurevar="Reproduced", groupvars="Stage3")
SummarySurv <- summarySE(Temp, measurevar="Survived", groupvars="Stage3")

Temp2 <- subset(Temp1, Survived == 1)
SummaryDay <- summarySE(Temp2, measurevar="DeathDay", groupvars="Stage3")


plot(1:4, SummaryRep1[,3], xaxt="n", ylim=c(0,.5), xlim=c(.8,5), type="b", pch=16, col="blue", xlab="Treatment", ylab="Proportion Reproduced", cex=1.4, lty=0, cex.lab=1.5, lwd=2)
axis(1, 1:4, labels=c("30.5", "32.5", "34.5","36.5"))
arrows(1:4, SummaryRep1[,3]-SummaryRep1[,"se"], 1:4, SummaryRep1[,3]+SummaryRep1[, "se"], code=3, angle=90, length=0.05, lwd=2, col="blue")
```
#2.Significance
##Survival
```{r}
model<-glm(Survived~Stage3,family=binomial(link='logit'),data=Temp)
anova(model, test="Chisq")
summary(model)

lsm<-lsmeans(model, list( ~ Stage3))
plot(lsm)

library(survival)

#This is the code for survival analysis, it will not run when all of the ones on the final day survived, so Kaylin's suggestion will work
#survdiff(Surv(DeathDay, Survived) ~ Ratio, InVitro)

#This is the analysis for death day if all survived from the final day.
model<-glm(DeathDay~Stage3,family=poisson(link='log'),data=Temp2)
anova(model, test="Chisq")
summary(model)

lsm<-lsmeans(model, list( ~ Stage3))
plot(lsm)

```

```{r}
Rmodel<-glm(Reproduced~Stage3,family=binomial(link='logit'),data=Temp2)
anova(Rmodel, test="Chisq")
summary(Rmodel)

lsm<-lsmeans(Rmodel, list( ~ Stage3))
plot(lsm)
```
